\chapter{Conclusion and Future Work}
\label{ch:conclusion}

\section{Summary of Contributions}
\section{Summary of Contributions}

Software maintenance research often emphasizes production code, although test code also plays an important role in software maintenance. This thesis contributes to test-code maintenance research along two dimensions: technical debt in test code and test-method evolution. For technical debt, the thesis shows that SATD in test code is uncommon but diverse, includes test-specific categories not fully captured by production-code SATD, and remains difficult for existing detectors and large language models to identify reliably. For method evolution, the thesis shows that reliable method-history evidence requires carefully validated oracles, and that \textit{HistoryFinder} provides the strongest overall support for reconstructing method histories among the evaluated research tools. Using validated test-method histories and method-level production-to-test mappings, the thesis further shows that many test methods evolve as frequently as, or more frequently than, the production methods they exercise, and that highly revised test methods are associated with more test smells. Together, these findings show that test code has maintenance concerns, detection challenges, and evolution patterns that are not fully captured by production-code assumptions. They also provide a foundation for future research on technical debt and evolution.

% Software maintenance research often emphasizes production code, although test code also plays an important role in software maintenance. This thesis contributes to test-code maintenance research along two dimensions: technical debt in test code and test-method evolution. For technical debt, it characterizes self-admitted technical debt (SATD) in test code by developing a test-specific taxonomy and a manually curated dataset, and by evaluating the effectiveness of existing tools and large language models for SATD detection and classification. For method evolution, it constructs validated method-history oracles and introduces \textit{HistoryFinder} to support reliable method-level history generation. It then uses validated test-method histories and method-level production-to-test mappings to study how test methods evolve in relation to the production methods they exercise. It also examines how test smells are associated with highly revised test methods. Together, the findings show that test code has maintenance concerns, detection challenges, and evolution patterns that are not fully captured by production-code assumptions. They also provide a foundation for future research on technical debt and evolution.

\subsection{Characterizing Self-Admitted Technical Debt in Test Code}

The SATD contribution characterizes how developers admit technical debt in test code by manually identifying relevant comments and classifying them into 12 categories, including four not captured by the source-code SATD taxonomies.

The findings show that this form of debt is uncommon but diverse. Some comments resemble known production-code debt categories, whereas others reflect test-specific concerns such as skipped tests and limited tests. Existing SATD detectors and large language models are also not yet reliable enough for detecting such debt in test comments. Overall, this contribution provides a test-specific taxonomy, a manually curated dataset, and empirical evidence on the limitations of current detection approaches.

\subsection{Generating Reliable Method-History}

The method-history work improves the reliability of method-level history generation. It shows that existing method-history oracles contain missing or incorrect revisions, which can affect conclusions about tool accuracy. To address this problem, the thesis constructs systematically validated oracles by combining the outputs of multiple tools with manual validation.

Using these oracles, the evaluation revisits existing method-history tools and introduces \textit{HistoryFinder}. The results show that \textit{HistoryFinder} provides the strongest overall balance of precision, recall, F1 score, and runtime among the evaluated research tools. This contribution strengthens the empirical foundation for method-level maintenance research and provides reusable support for studying how individual methods evolve.

\subsection{Understanding Test Method Evolution}

To assess whether existing method-history tools can support test-method evolution analysis, a manually validated oracle of test-method histories is constructed. The evaluation shows that tools developed for production code method history generation can also generalize to test code, with \textit{HistoryFinder} achieving the strongest overall performance. Method-level production-to-test mapping techniques are also evaluated, showing that no single approach dominates: some provide higher precision, whereas others provide broader recall.

The evolution analysis shows that test methods are not merely passive reflections of production-code change. Many test methods are revised as often as, or more often than, their corresponding production methods. Highly revised test methods also tend to contain more test smells, with the strongest association observed among small methods. These findings indicate that test methods have their own maintenance dynamics and should be studied as independently evolving software artifacts.

\section{Future Work}

\subsection{Improving Test-Code SATD Detection}

Future work should develop SATD detection approaches that are designed specifically for test comments and capable of learning test-specific expressions. Large language models also require more test-aware adaptation. It should investigate richer contextual inputs, such as surrounding test code, to better distinguish genuine SATD from ordinary explanatory comments.

Once test-code SATD can be detected more reliably, future work can also develop automated classification techniques based on the proposed taxonomy. Reliable detection and classification would enable larger-scale studies of the long-term maintenance impact of test-code SATD, such as whether affected tests are more likely to be changed or associated with later defects than comparable tests without SATD.

\subsection{Extending Method-History Generation}

Scalability can be improved by reducing the cost of method extraction during history construction. \textit{HistoryFinder} currently relies on \texttt{JavaParser} to extract method-level information from \texttt{Git} revisions. Because this parsing is repeated across many revisions and methods, it can increase construction time for large repositories or when histories are generated for hundreds of thousands of methods. A more efficient alternative is low-level direct parsing, which would extract only the method information needed for tracking.

Method-history generation should also be extended beyond Java to evaluate whether current approaches generalize to other programming languages. This extension may require adjusting similarity thresholds for language-specific matching.

\subsection{Building History-Aware Test Maintenance Tools}

The findings of this thesis can inform practical tools that combine SATD comments, method histories, production-to-test mappings, and test smells. Such tools could help developers identify tests that contain self-admitted debt, are revised frequently, evolve differently from the production methods they exercise, or show signs of quality problems. History-aware tools could also support test maintenance tasks such as regression-test prioritization and obsolete test detection.

\section{Concluding Remarks}

This thesis shows that test code deserves direct attention in software maintenance research. By studying SATD in test code, building reliable method-history evidence, and analyzing method-level test-code evolution, the thesis demonstrates that test code contains maintenance concerns and evolution patterns that cannot be fully understood through production-code assumptions alone.

Overall, the thesis contributes to a broader view of software maintenance in which test code receives direct attention as a maintained software artifact. Advancing this view can help researchers build stronger empirical models and help practitioners maintain test suites that remain reliable, useful, and trustworthy over time.
