\chapter{Self-Admitted Technical Debt in Test Code: Taxonomy and Detection}
\label{ch:td}


\newcommand{\xmark}{\ding{55}}

%%%Author definitions
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%

\tikzset{
  box/.style = {rectangle, draw=black, rounded corners, minimum width=28mm, minimum height=8mm, align=center, font=\sffamily},
  smallbox/.style = {rectangle, draw=black, rounded corners, minimum width=22mm, minimum height=7mm, align=center, font=\sffamily\footnotesize},
  arrow/.style = {-{Stealth[length=3mm]}, semithick},
  grouped/.style = {draw=black,dashed,rounded corners,inner sep=6pt},
  arrowicon/.style = {font=\small} % icons above arrow
}

%% for presenting comments
\lstset{
  language=Java,
  basicstyle=\ttfamily\small,
  commentstyle=\color{black}\itshape,
  keywordstyle=\color{blue},
  stringstyle=\color{orange},
  showstringspaces=false,
  frame=none,
  tabsize=2,
  breaklines=true
}

\input{command/command}

%%
% %% \BibTeX command to typeset BibTeX logo in the docs
% \AtBeginDocument{%
%   \providecommand\BibTeX{{%
%     Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%% These commands are for a PROCEEDINGS abstract or paper.
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}



% \definecolor{commentColor}{RGB}{106,135,89}
\definecolor{commentColor}{rgb}{0.0, 0.35, 0.0}


This chapter contributes to the first part of this thesis, which examines technical debt in test code. It focuses on self-admitted technical debt (SATD), a form of technical debt explicitly documented by developers in source-code comments. In the context of test code, these comments capture maintenance concerns such as incomplete tests, postponed improvements, limitations, workarounds, and known quality issues. This chapter investigates how SATD appears in test code, develops a taxonomy of test-code SATD, and evaluates whether existing SATD detection techniques can effectively identify such debt.

This chapter is based on the following manuscript:
\begin{itemize}
\item S. Islam, M. N. I. Opu, S. Wang, and S. Chowdhury, ``A First Look at Self-Admitted Technical Debt in Test Code: Taxonomy and Detection,'' manuscript under review, 2026.
\end{itemize}

The study analyzes 50,000 comments sampled from 1.6 million test-code comments across 1,000 open-source Java projects. It constructs a taxonomy of SATD in test code and evaluates the effectiveness of existing SATD detectors, as well as open-source and proprietary large language models, for detecting test-code SATD.

The main takeaways from this chapter are as follows:
\begin{itemize}
\item SATD in test code is relatively uncommon but diverse, covering both general maintenance concerns and test-specific issues.
\item Existing SATD detectors and large language models are not yet reliable enough for test-code SATD detection without further test-aware adaptation.
\item The curated test-code SATD dataset and taxonomy provide a foundation for future studies on test-code quality, technical debt, and automated SATD detection.
\end{itemize}

\textbf{Impact:} Since the manuscript is currently under review, its publication impact cannot yet be assessed. Within this thesis, this chapter establishes the technical-debt part by showing that SATD in test code includes test-specific categories and expressions that are not fully captured by production-code SATD knowledge. It also provides a curated dataset and taxonomy that can support future research on test-code quality, technical debt, and automated SATD detection.



\section*{Abstract}
Self-admitted technical debt (SATD) refers to comments in which developers explicitly acknowledge code issues, workarounds, or suboptimal solutions. SATD is known to significantly increase software maintenance effort. While extensive research has examined SATD in source code, its presence and impact in test code have received no focused attention, leaving a significant gap in our understanding of how SATD manifests in testing contexts.

This study investigates SATD in test code by manually analyzing 50,000 comments randomly sampled from 1.6 million comments across 1,000 open-source Java projects. From this sample, after manual analysis and filtering, we identified \totalSatdCount{} SATD comments and classified them into \categoryCount{} distinct categories, building a taxonomy of test code SATD. To investigate whether test code SATD can be detected automatically, we evaluated existing SATD detection tools, as well as both open-source and proprietary LLMs. Among the existing tools, MAT performed the best, albeit with moderate recall. To our surprise, both open-source and proprietary LLMs exhibited poor detection accuracy, primarily due to low precision. These results indicate that neither existing approaches nor current LLMs can reliably detect SATD in test code.

Overall, this work provides the results of a large-scale analysis of SATD in test code, a nuanced understanding of its types, and the limitations of current SATD detection methods. Our findings lay the groundwork for future research on test code-specific SATD.


\input{section/1_Introduction}
\input{section/2_Related_Work}
\input{section/3_Methodology}
\input{section/4_Approach_and_Results}
\input{section/5_Discussion_and_Limitation}
