\chapter{Introduction}
\label{ch:intro}

Software maintenance is a continuous and expensive part of the software life cycle. After initial development, software systems must be corrected, adapted, improved, and extended to keep them operational, reliable, and aligned with changing requirements, platforms, dependencies, and user expectations~\cite{kafura_use_1987, borstler_role_2016, sokolowski2022change, zhang2024developers}. This maintenance effort applies not only to production code but also to test code. Since test code is used to check the correctness of production code, its own correctness and maintainability are equally important. If tests are incorrect, outdated, or difficult to maintain, they may fail to detect regressions, report false failures, or provide developers with misleading confidence. Therefore, test code should not be treated as a secondary artifact; it deserves research and maintenance attention comparable to production code.

To support software maintenance, researchers have developed indicators and tools that help identify artifacts requiring developer attention. These indicators include source-code metrics, code smells, bug histories, change histories, and self-admitted technical debt. Prior studies have used such indicators to identify change-prone, bug-prone, or maintenance-prone artifacts~\cite{romano_using_2011, khomh_exploratory_2009, pascarella_performance_2020, chowdhury_method-level_2024, chowdhury_good_2025}. Among these indicators, two are particularly relevant to understanding maintenance needs: self-admitted technical debt, which captures maintenance concerns explicitly documented by developers, and method-level change history, which shows how individual methods evolve over time. However, both lines of research have focused mainly on production code or datasets dominated by production code.

This production-code focus leaves important questions about test code unanswered. Although prior studies have shown that test code has its own quality and maintenance concerns, including test smells, cloning, identifier-quality issues, and co-evolution with production code~\cite{bavota_are_2015, tufano_empirical_2016, lin_quality_2019, counsell_comparing_2016, van_bladel_comparative_2023, zaidman_studying_2011, spadini_relation_2018}, we still know less about how technical debt appears in test code and how test methods evolve over time. This gap matters because poorly maintained tests can become ineffective, obsolete, flaky, difficult to understand, or costly to update~\cite{pinto2012understanding, hao2013bug, bhatta2025understanding, yaraghi2025automated}.

This thesis addresses this gap by studying test-code maintenance from two complementary perspectives. First, it investigates self-admitted technical debt (SATD) in test code, where developers explicitly record maintenance concerns, shortcuts, workarounds, or future work in comments. Second, it investigates method-level test-code evolution, focusing on how test methods change over time and how their evolution relates to the production methods they exercise. Together, these two perspectives provide a more detailed understanding of test-code maintenance and help build stronger empirical foundations for future research on test-code quality and evolution.


\section{Background and Motivation}

\subsection{Technical Debt in Test Code}

Technical debt refers to suboptimal implementation decisions that may provide short-term benefits but increase future maintenance costs~\cite{seaman_technical_2015}. A particular form of technical debt is self-admitted technical debt (SATD), where developers explicitly document debt, shortcuts, workarounds, uncertainty, or postponed work in code comments~\cite{potdar_exploratory_2014}. Potdar and Shihab~\cite{potdar_exploratory_2014} were among the first to systematically study SATD in open-source projects, and Maldonado and Shihab~\cite{maldonado_detecting_2015} later classified SATD comments into categories such as design, requirement, defect, test, and documentation debt. Subsequent studies showed that SATD can persist over time~\cite{bavota_large-scale_2016}, negatively affect software evolvability~\cite{wehaibi_examining_2016}, and be associated with larger, more complex, less readable, more change-prone, and more bug-prone methods~\cite{chowdhury_evidence_2025}.

Because SATD captures maintenance concerns explicitly written by developers, it has received considerable research attention. Prior studies have proposed techniques for detecting SATD~\cite{maldonado_detecting_2015, liu_satd_2018, huang_identifying_2018, li_automatic_2023, sheikhaei_empirical_2024, maldonado_using_2017, gama_towards_2024, rantala_prevalence_2020}, classifying SATD~\cite{zhu_detecting_2021, maldonado_detecting_2015, obrien_artifact_2022, bhatia_empirical_2025}, and mitigating or tracking SATD over time~\cite{maldonado_empirical_2017, zampetti_was_2018, zampetti_automatically_2020, iammarino_empirical_2021, liu_exploratory_2021, mastropaolo_towards_2023}. Researchers have also extended SATD studies to specialized domains, including machine learning software~\cite{obrien_artifact_2022, bhatia_empirical_2025}, Dockerfiles~\cite{azuma_empirical_2022}, blockchain projects~\cite{pinna_investigation_2023}, and Android applications~\cite{wilder_exploratory_2023}. However, the subject systems and datasets used in most SATD studies have been either exclusively production code or overwhelmingly dominated by production code. Counsell and Swift~\cite{counsell_timing_2022} examined SATD in both test and production classes, but their focus was the timing of SATD introduction rather than the characterization or detection of SATD in test code.

Relying on findings from production-code SATD to understand test-code SATD may lead to incomplete or inaccurate conclusions. Test code differs from production code in several important ways. Prior studies have shown that test code can contain test-specific code smells~\cite{bavota_are_2015, tufano_empirical_2016}, exhibit a higher prevalence of cloning~\cite{van_bladel_comparative_2023}, and contain comments less frequently than production code~\cite{counsell_comparing_2016}. Moreover, developers may devote less attention to the quality of test code than to production code, which can result in obsolete, fragile, difficult-to-maintain, or low-quality tests~\cite{counsell_comparing_2016, beller_developer_2019, beller_when_2015, zaidman_studying_2011, athanasiou_test_2014, spadini_relation_2018}. These differences suggest that SATD in test code may have different forms, causes, and detection challenges than SATD in production code.

Therefore, SATD in test code remains insufficiently understood. It is still unclear whether SATD in test code follows the same patterns as SATD in production code, whether production-oriented SATD taxonomies are sufficient for test code, and whether existing SATD detectors or large language models can reliably identify SATD in test comments. This motivates the first part of this thesis, which characterizes SATD in test code and evaluates the effectiveness of existing tools and models for detecting it.

\subsection{Method-Level History and Test-Code Evolution}

Software evolution histories provide valuable evidence for understanding how software systems change over time. Practitioners use code histories for tasks such as provenance analysis, traceability, code comprehension, developer onboarding, code review, and expert identification~\cite{grund_codeshovel_2021}. Researchers use them to study and build maintenance models for tasks such as bug prediction, change prediction, clone management, technical debt analysis, authorship attribution, and maintenance effort estimation~\cite{duala-ekoko_tracking_2007, kashiwabara_method_2015, meng_mining_2013, rahman_ownership_2011, pascarella_performance_2020, chowdhury_method-level_2024, chowdhury_good_2025, chowdhury_evidence_2025}. However, version control systems such as \texttt{Git} primarily record changes at the file level, whereas many maintenance questions require finer granularity. For example, understanding whether a specific method is change-prone, bug-prone, or affected by technical debt requires reconstructing how that method evolved across commits.

Prior work has therefore proposed tools for fine-grained and method-level history reconstruction. \textit{Historage}~\cite{hata_historage_2011} and \textit{FinerGit}~\cite{higo_tracking_2020} enable method-level analysis by restructuring repositories so that individual program elements can be tracked more precisely. However, these approaches require substantial preprocessing before histories can be generated. To support on-demand method-history extraction, Grund \textit{et al.}~\cite{grund_codeshovel_2021} introduced \textit{CodeShovel}, which tracks Java method histories using lightweight similarity-based heuristics. Jodavi \textit{et al.}~\cite{jodavi_accurate_2022} later identified inaccuracies in the \textit{CodeShovel} oracle, corrected part of the benchmark, and introduced \textit{CodeTracker}, a refactoring-aware method-history tool.

These studies show that method-level history reconstruction is both important and difficult. Methods can be renamed, moved, refactored, or substantially modified across commits~\cite{higo_tracking_2020, grund_codeshovel_2021, jodavi_accurate_2022}. Moreover, evaluations of method-history tools depend heavily on the quality of the oracles used as ground truth. Recent tools such as \textit{CodeShovel} and \textit{CodeTracker} were evaluated using manually constructed or manually corrected method-history oracles. \textit{CodeShovel} relied on a human-generated oracle, while \textit{CodeTracker} was evaluated using an extended and corrected version of that oracle with support from \textit{RefactoringMiner}~\cite{grund_codeshovel_2021, jodavi_accurate_2022}. Although manual validation is essential for building reliable benchmarks, reconstructing complete method histories is itself error-prone because annotators must inspect changes across many commits, refactorings, renames, and file moves. If such oracles contain false positives or false negatives, then conclusions about tool accuracy may be unreliable. Such inaccuracies can also affect downstream research that uses method histories to study change-proneness, bug-proneness, technical debt, or maintenance effort. Therefore, accurate method-level history reconstruction requires both reliable tools and reliable evaluation oracles. This motivates the second study of this thesis, which constructs systematically validated method-history oracles and introduces \textit{HistoryFinder}, a method-level history generation tool designed to improve accuracy while maintaining competitive runtime.

Reliable method histories are also essential for studying test-code evolution. Prior research has examined how production and test code co-evolve~\cite{zaidman2011studying, wang2021understanding, sun_revisiting_2023}, why test suites change~\cite{pinto2012understanding}, how test smells relate to test maintainability~\cite{Spadini:2018}, and why tests are deleted or become obsolete~\cite{hao2013bug, bhatta2025understanding, yaraghi2025automated}. However, many of these studies are constrained by the lack of validated test method histories. For example, Pinto \textit{et al.}~\cite{pinto2012understanding} reported that tracking test methods is challenging because tests are frequently renamed or moved. Bhatta \textit{et al.}~\cite{bhatta2025understanding} relied on custom heuristics, refactoring detection, and extensive manual inspection to identify deleted tests, limiting scalability. Similarly, Spadini \textit{et al.}~\cite{Spadini:2018} studied the association between test smells and test evolution, but their history reconstruction relied on an unevaluated heuristic. Although recent method-history tools have improved history reconstruction for production methods, their effectiveness on test methods remains unclear because they were primarily developed and evaluated using production-code oracles. Therefore, before using these tools to study test-code evolution, we first need a reliable oracle of test method histories and an empirical evaluation of state-of-the-art history-tracking tools on test methods.


Tracking test method histories alone, however, is not sufficient to understand why test methods evolve. A test method often changes because the production method it exercises has changed, but it may also change because of issues internal to the test itself, such as poor design, fragility, obsolete assertions, or test smells. Distinguishing between these possibilities requires method-level links between test methods and the production methods they exercise. Without such mappings, it is difficult to determine whether a test revision is induced by production-code evolution or by independent test-code maintenance needs. Method-level production-to-test mappings can also support finer-grained studies of production--test co-evolution and obsolete test detection, because they can identify which specific test methods are affected by changes to particular production methods rather than only identifying affected files or classes.

Several approaches have been proposed for production-to-test mapping, including naming conventions, call-based heuristics, dynamic traces, and static traceability techniques~\cite{van_rompaey_establishing_2009, white_establishing_2020, white_tctracer_2022, sun_method-level_2024}. However, each approach has limitations. Dynamic approaches can provide useful runtime evidence, but they require projects to compile and tests to execute. Static approaches are more scalable, but they may miss relevant links or include incidental helper calls that do not represent the behavior under test~\cite{white_tctracer_2022, sun_method-level_2024}. Therefore, before test-code evolution can be studied accurately at the method level, we need to evaluate both method-history tools on test methods and production-to-test mapping techniques against reliable benchmarks.

Taken together, these limitations reveal three main research gaps. First, existing SATD research provides limited evidence about how developers admit technical debt in test code. Production-oriented SATD taxonomies and detectors may not capture test-specific debt types, and the effectiveness of recent large language models for detecting test-code SATD remains unclear. Second, method-level history generation still suffers from oracle and tooling limitations. If method-history oracles are inaccurate, then evaluations of history-tracking tools and downstream studies that rely on those histories may also be unreliable. Third, test-code evolution has not been sufficiently studied using validated test method histories and method-level production-to-test links. Without these foundations, it is difficult to determine whether test methods mainly evolve in response to production code or whether they also change due to their own maintenance concerns.

Therefore, the objective of this thesis is to improve our understanding of test code by investigating its technical debt and method-level evolution. Specifically, this thesis studies SATD in test code, develops and evaluates accurate method-history generation support, and uses validated histories and production-to-test links to analyze how test methods evolve relative to the production methods they exercise. The thesis focuses on open-source Java systems and uses method-level analysis as the primary granularity because methods are small enough to capture fine-grained maintenance behavior but large enough to represent meaningful units of developer work.


\section{Thesis Contributions}

This thesis makes three main contributions, corresponding to the three research studies presented in the following chapters.

\subsection{Self-Admitted Technical Debt in Test Code}

The first contribution is a large-scale empirical study of SATD in test code. Chapter~\ref{ch:td} manually analyzes 50,000 test-code comments sampled from 1.6 million comments across 1,000 open-source Java projects. The study identifies SATD comments in test code, classifies them into a taxonomy that includes test-specific categories, and evaluates existing SATD detection tools as well as open-source and proprietary large language models.

The results show that test-code SATD has characteristics that are not fully captured by production-code SATD taxonomies or detectors. Existing SATD tools can provide useful precision but limited recall, while the evaluated large language models struggle to provide reliable precision-recall trade-offs for this task. This contribution provides a manually curated dataset, a test-code SATD taxonomy, and empirical evidence that can support future research on test-aware SATD detection and classification.

\subsection{Accurate Method-Level History Generation}

The second contribution is a methodological foundation for accurate method-level evolution research. Chapter~\ref{ch:hf} constructs systematically developed method-history oracles using a semi-automated process that combines multiple state-of-the-art tools with expert manual validation. It also introduces \textit{HistoryFinder}, a method-level history generation tool designed to improve accuracy while maintaining competitive runtime performance.

The evaluation shows that \textit{HistoryFinder} provides a strong overall balance of precision, recall, F1 score, and runtime among the evaluated research tools. This contribution improves both the benchmark data and the tool support needed for method-level maintenance studies, including studies of change-proneness, bug-proneness, technical debt, and test-code evolution.

\subsection{Method-Level Test-Code Evolution}

The third contribution is a method-level empirical study of test-code evolution. Chapter~\ref{ch:t2p} first evaluates whether state-of-the-art method-history tools can accurately track test method histories using a manually constructed oracle of 120 test methods from 40 open-source Java projects. It then evaluates method-level production-to-test mapping approaches using existing benchmarks and a newly constructed oracle. Using the most suitable history-tracking and mapping approaches, the study compares the revision frequencies of test methods and their corresponding production methods and examines whether test smells are associated with highly revised test methods.

The results challenge the common assumption that test code primarily changes in response to production code. A substantial portion of test methods undergo as many or more revisions than their corresponding production methods, and highly revised small test methods show stronger associations with test smells. This contribution provides a more precise empirical basis for future research on test maintenance, regression testing, obsolete test detection, test repair, and test smell management.

Overall, this thesis makes the following contributions:

\begin{itemize}
\item It provides a manually curated dataset and taxonomy of SATD in test code and evaluates the ability of existing SATD tools and large language models to detect test-code SATD.
\item It constructs reliable method-level history oracles and introduces \textit{HistoryFinder}, a method-history generation tool with strong accuracy and competitive runtime.
\item It evaluates method-history tools on test methods and evaluates method-level production-to-test mapping techniques using manually constructed benchmarks.
\item It presents a method-level empirical study showing how test methods evolve relative to the production methods they exercise and how test smells are associated with highly revised test methods.
\end{itemize}

\section{Thesis Organization}

The remainder of this thesis is organized as follows.

Chapter~\ref{ch:td} presents the study of self-admitted technical debt in test code. It describes the collection and manual analysis of test-code comments, presents a taxonomy of test-code SATD, and evaluates existing SATD detectors and large language models for identifying SATD in test comments.

Chapter~\ref{ch:hf} presents the work on method-level history generation. It discusses limitations in existing method-history oracles, describes the construction of new oracles, introduces \textit{HistoryFinder}, and evaluates method-history tools in terms of precision, recall, F1 score, and runtime.

Chapter~\ref{ch:t2p} presents the study of method-level test-code evolution. It evaluates method-history tools on test methods, evaluates production-to-test method linking approaches, compares the revision frequencies of test and production methods, and analyzes the association between test smells and highly revised test methods.

Chapter~\ref{ch:conclusion} concludes the thesis by summarizing the findings, discussing their implications for test-code maintenance research, and outlining directions for future work.
