\section{Threats to Validity}
% \textit{Internal Validity.}
% The construction of the method-history oracle and the test-to-production method-mapping ground truths is impacted by human judgment. This threat was mitigated to some extent as we used two different annotators.

% \textit{External Validity.}
% The main external threat is project selection. Because our study used open-source Java projects, the results may not fully generalize to closed-source or industrial systems, or to projects written in other programming languages.

\emph{Construct Validity.} The analyses relied on method-level history generation, production-to-test mapping, and test-smell detection. Some of the relevant threats were mitigated by first evaluating existing history-generation and mapping techniques on manually constructed oracles and then using the best-performing approaches in the subsequent analyses.

\emph{Internal Validity.} The change-history and production-to-test mapping oracles involved human judgment. To mitigate this threat, two authors independently performed the annotations and resolved disagreements through discussion.

\emph{External Validity.} The dataset includes 110 open-source Java projects. Although this is substantially larger than the datasets used in prior work, the findings may not generalize to closed-source systems and other programming languages. Also, due to focusing on a precision-oriented approach for mapping between production and test, many examples were missed, which may harm generalizability.

\emph{Conclusion Validity.} Appropriate non-parametric statistical tests, effect sizes, confidence intervals, and false-discovery-rate correction were used where applicable. However, as with many observational studies, the findings confirm associations rather than guaranteed causal relationships.
