\chapter{Test Method Evolution: Histories, Production-to-Test Mapping, and Test Smells}
\label{ch:t2p}

The third contribution of this thesis builds on the method-history support developed in Chapter~\ref{ch:hf} and applies it to test-code evolution. Rather than examining test code only at the file or class level, this chapter analyzes how individual test methods evolve over time. It combines method-history generation with method-level production-to-test mapping to examine whether test methods mainly change in response to the production methods they exercise or whether they also exhibit independent maintenance patterns.

This chapter is based on the following manuscript:
\begin{itemize}
\item S. Islam, A. Waseem, and S. Chowdhury, ``Understanding Method-Level Test Code Evolution,'' manuscript under review, 2026.
\end{itemize}

This chapter first evaluates whether existing method-history generation tools can accurately reconstruct test-method histories using a manually constructed oracle of 120 test methods from 40 open-source Java projects. It then evaluates method-level production-to-test mapping techniques using existing benchmarks and a newly constructed oracle. Using the most suitable history-tracking and mapping approaches, this chapter conducts a large-scale analysis across 110 projects to compare the revision frequencies of test methods and their corresponding production methods and to examine the association between test smells and highly revised test methods.

The main takeaways from this chapter are as follows:
\begin{itemize}
\item Existing method-history tools can effectively track test-method histories, with \emph{HistoryFinder} providing the strongest overall performance.
\item Static method-level production-to-test mapping techniques involve precision-recall trade-offs, so the most suitable approach depends on the downstream study goal.
\item Many test methods evolve as much as or more than their corresponding production methods, suggesting that test methods are not always changed only as a reaction to production-code changes.
\item Highly revised small test methods show stronger associations with test smells, indicating that some test-code evolution may be related to test-specific maintenance concerns.
\end{itemize}

\textbf{Impact:} This chapter provides empirical evidence and methodological resources for future studies of test-code evolution. Its manually constructed test-method history oracle can support future evaluations of method-history generation tools on test code, while its production-to-test mapping oracle can support more precise studies of production--test co-evolution. The large-scale findings also suggest that future research should treat test methods as independently evolving maintenance artifacts rather than assuming that test-code changes are always driven by production-code changes.


\clearpage

\section*{Abstract}
% Accurately tracking test code change history at the method level is crucial for effective test maintenance and evolution research including understanding test suite evolution, obsolete test detection, and automated test repair.
% Software evolution histories are crucial for understanding software maintenance and developing maintenance tools and models.
Although recent advances in method-level history tracking enabled fine-grained studies of production code evolution, research on test code evolution remains constrained by two challenges: the lack of validated approaches for reconstructing test method histories and limited knowledge of the most effective techniques for method-level production-to-test mapping. This contribution addresses both challenges to enable accurate studies of test code evolution. It first evaluates state-of-the-art method history tracking tools using a manually constructed oracle of 120 test methods from 40 open-source Java projects. It then assesses static analysis-based production-to-test mapping techniques using existing benchmarks and a newly created oracle. Leveraging the most suitable approaches, it conducts a large-scale empirical study of test method evolution by comparing the revision frequencies of test methods and the production methods they exercise.

The results show that nearly 55\% of test methods undergo as many or more revisions than their corresponding production methods, challenging the common assumption that test code primarily evolves in response to production code changes. Further analysis reveals that highly change-prone yet small test methods exhibit substantially higher concentrations of test smells than other test methods. In general, the results demonstrate a more accurate approach to capturing test code change history that can help future studies on test suite evolution, test deletion and obsolescence, and automated test repairs.


\clearpage

\input{1-introduction}
\input{2-related-work}
\input{3-study-setup}

\section{Approach and Results}
\label{sec:approach-results}
The approach and results of each RQ are discussed below.
\input{4.1-rq1-method-history-oracle}
\input{4.2-rq2-method-linking}
\input{4.3-rq3-test-vs-production-method-revision}
\input{4.4-rq4-test-smell-association}
\input{5-discussion}
\input{6-threat-to-validity}
\input{7-conclusion}
