\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

First and foremost, I express my deepest gratitude to Almighty God for giving me strength, patience, and perseverance in all aspects of my life.

I am grateful to my supervisor, Professor Shaiful Chowdhury, for his guidance, encouragement, valuable feedback, and continuous support throughout this research journey. His advice and mentorship have played an important role in shaping this work.

I would also like to thank my thesis committee members, Professor Shaowei Wang and Professor Hamid Mansoor, for their time and support.

I also gratefully acknowledge the people of Bangladesh, whose contributions through public funding supported my undergraduate education. That support helped build the foundation that made this academic journey possible.

I would like to thank my lab mates for their support, discussions, and encouragement throughout this journey.

I express my appreciation to my friends and industry colleagues, especially Minaoar Hossain Tanzil, whose encouragement and support helped shape the beginning of this academic journey. Their collaboration, encouragement, and professional experiences contributed to my growth and helped prepare me for this research journey.

I am deeply thankful to my family and relatives for their love, sacrifices, constant encouragement, and motivation during difficult times.

Finally, I am deeply grateful to my beloved wife for her love, patience, understanding, and unwavering support throughout this journey.