\chapter*{Contributions of Authors}
\addcontentsline{toc}{chapter}{Contributions of Authors}

This thesis follows a grouped manuscript format and contains three manuscripts. The nature and extent of the candidate's contribution and the contributions of the co-authors are described below.


\section*{Manuscript 1 (Chapter~\ref{ch:td}): A First Look at the Self-Admitted Technical Debt in Test Code: Taxonomy and Detection}
\addcontentsline{toc}{section}{Manuscript 1 (Chapter~\ref{ch:td}):}
\textbf{Authors:} Shahidul Islam, Md Nahidul Islam Opu, Shaowei Wang, Shaiful Chowdhury.\\
\textbf{Status:} Under review at The Journal of Systems \& Software.\\
\textbf{Candidate's contribution:} Was responsible for the implementation, data collection, analysis, and writing. Contributed to the study design, response to reviewers, and manual SATD identification and classification.\\
\textbf{Co-authors' contributions:} Shaiful Chowdhury and Shaowei Wang provided supervision, conceptual guidance, and feedback on the study. Md Nahidul Islam Opu and Shaiful Chowdhury contributed to the initial manual identification and classification of a subset of SATD comments.

\section*{Manuscript 2 (Chapter~\ref{ch:hf}): HistoryFinder: Advancing Method-Level Source Code History Generation with Accurate Oracles and Enhanced Algorithm}
\addcontentsline{toc}{section}{Manuscript 2 (Chapter~\ref{ch:hf}):}
\textbf{Authors:} Shahidul Islam, Ashik Aowal, Md Sharif Uddin, Shaiful Chowdhury.\\
\textbf{Status:} Published in the Proceedings of the 48th IEEE/ACM International Conference on Software Engineering (ICSE 2026).\\
\textbf{Candidate's contribution:} Was responsible for the problem formulation, methodology and study design, implementation, data collection, oracle construction and validation, analysis, writing, revision, and response to reviewers.\\
\textbf{Co-authors' contributions:} Shaiful Chowdhury provided supervision, conceptual guidance, methodology feedback, manuscript feedback, and response to reviewers. Ashik Aowal supported manual validation of method-history oracles. Md Sharif Uddin contributed to algorithmic design.


\section*{Manuscript 3 (Chapter~\ref{ch:t2p}): Understanding Method-Level Test Code Evolution}
\addcontentsline{toc}{section}{Manuscript 3 (Chapter~\ref{ch:t2p}):}
\textbf{Authors:} Shahidul Islam, Anusha Waseem, Md Nahidul Islam Opu, Shaiful Chowdhury.\\
\textbf{Status:} Under review at the 49th IEEE/ACM International Conference on Software Engineering.\\
\textbf{Candidate's contribution:} Was responsible for the problem formulation, methodology and study design, implementation, data collection, production-to-test mapping setup, analysis, and writing. Contributed to the manual validation and annotation of test-method histories and production-to-test links.\\
\textbf{Co-authors' contributions:} Shaiful Chowdhury provided supervision, conceptual guidance, methodology feedback, and manuscript writing. Anusha Waseem supported oracle labelling. Md Nahidul Islam Opu supported validation of the implementation.
