\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

This thesis is based on three research manuscripts, one of which has been published and two of which are currently under review. I was the main contributor to these manuscripts under the supervision of Professor Shaiful Chowdhury. I designed the methodology in consultation with Professor Shaiful Chowdhury, conducted the experiments, analyzed the results, and contributed to the writing of the manuscripts. In some cases, my collaborators assisted with the annotation of the data.

Chapter~\ref{ch:td} of this thesis is based on the following manuscript:
\begin{quote}
\begin{itemize}
    \item S. Islam, M. N. I. Opu, S. Wang, and S. Chowdhury, “A First Look at Self-Admitted Technical Debt in Test Code: Taxonomy and Detection,” manuscript under review, 2026.
    \end{itemize}
\end{quote}

Chapter~\ref{ch:hf} of this thesis is based on the following manuscript:
\begin{quote}
\begin{itemize}
\item S. Islam, A. Aowal, M. S. Uddin, and S. Chowdhury, “HistoryFinder: Advancing Method-Level Source Code History Generation with Accurate Oracles and Enhanced Algorithm,” in Proceedings of the 48th IEEE/ACM International Conference on Software Engineering (ICSE 2026), Rio de Janeiro, Brazil, Apr. 2026.
\end{itemize}
\end{quote}


Chapter~\ref{ch:t2p} of this thesis is based on the following manuscript:

\begin{quote}
\begin{itemize}
\item S. Islam, A. Waseem, and S. Chowdhury, “Understanding Method-Level Test Code Evolution,” manuscript under review, 2026.
\end{itemize}
\end{quote}


Below is a list of my other co-authored publications completed during my MSc degree but not included in this thesis.

\begin{quote}
\begin{itemize}
    \item M. N. I. Opu, S. Islam, M. Asaduzzaman, and S. Chowdhury, “How Do Agentic AI Systems Address Performance Optimizations? A BERTopic-Based Analysis of Pull Requests,” in Proceedings of the 23rd International Conference on Mining Software Repositories (MSR 2026), Mining Challenge Track, Rio de Janeiro, Brazil, Apr. 2026
    \item M. N. I. Opu, S. Islam, S. Rouhani, and S. Chowdhury, “Understanding the Issue Types in Open Source Blockchain-Based Software Projects with the Transformer-Based BERTopic,” in Proceedings of the 2025 IEEE International Conference on Collaborative Advances in Software and Computing (CASCON), 2025
    \end{itemize}
\end{quote}


% The specific contributions of each author are described in the ``Contributions of Authors'' section.