\chapter{HistoryFinder: Reliable Oracle Construction and Method-History Generation}
\label{ch:hf}

This chapter begins Part~\ref{part:test-method-evolution} and presents the second contribution of this thesis: improving the reliability of method-level history generation. Many software-evolution studies rely on accurate histories of individual methods, including studies of change-proneness, bug-proneness, technical debt, and test-code evolution. In this thesis, such histories are also required for Chapter~\ref{ch:t2p}, where we evaluate test-method history construction and then study test-method evolution. Therefore, this chapter addresses two related methodological problems: constructing reliable method-history oracles and improving tool support for method-history generation.

This chapter is based on the following manuscript:
\begin{itemize}
\item S. Islam, A. Aowal, M. S. Uddin, and S. Chowdhury, ``HistoryFinder: Advancing Method-Level Source Code History Generation with Accurate Oracles and Enhanced Algorithm,'' in Proceedings of the 48th IEEE/ACM International Conference on Software Engineering (ICSE 2026), Rio de Janeiro, Brazil, Apr. 2026.
\end{itemize}

The study revisits the evaluation of method-level history generation tools by constructing two systematically validated oracles: a corrected \textit{CodeShovel} oracle and a new \textit{HistoryFinder} oracle. Using these oracles, the study evaluates existing tools to identify their strengths and limitations before introducing \textit{HistoryFinder}. The evaluation uses 400 methods from 40 open-source Java repositories and compares \textit{HistoryFinder} with \textit{CodeShovel}, \textit{CodeTracker}, \textit{IntelliJ}, and \texttt{Git}-based baselines in terms of precision, recall, F1 score, and runtime.

The main takeaways from this chapter are as follows:
\begin{itemize}
\item Existing method-history oracles contain missing and incorrect method revisions, which can affect conclusions about tool performance.
\item Systematically validated oracles provide a more reliable basis for evaluating method-history generation tools.
\item Existing tools have different strengths and limitations when evaluated against more reliable oracles.
\item \textit{HistoryFinder} provides the strongest overall balance of precision, recall, F1 score, and runtime among the evaluated research tools.
\item The oracles and tool developed in this chapter support Chapter~\ref{ch:t2p}, where \textit{HistoryFinder} is evaluated on test-method history construction and then applied to method-level test-code evolution.
\end{itemize}

\textbf{Impact:} This work has been published in the Proceedings of the 48th IEEE/ACM International Conference on Software Engineering (ICSE 2026). Within this thesis, this chapter improves both benchmark quality and tool support for method-history generation. More broadly, its validated oracles and \textit{HistoryFinder} tool can support empirical studies that require accurate method histories, including studies of change-proneness, bug-proneness, technical debt, maintenance effort, code ownership, and software evolution. In this thesis, the contribution is further used in Chapter~\ref{ch:t2p} to study test-code evolution at the method level.



\section*{Abstract}
Reconstructing a method’s change history efficiently and accurately is critical for many software engineering tasks, including maintenance, refactoring, and comprehension. Despite the availability of method history generation tools such as \textit{CodeShovel} and \textit{CodeTracker}, existing evaluations of their effectiveness are limited by inaccuracies in the ground truth oracles used. In this study, we systematically construct two new oracles—the corrected \textit{CodeShovel} oracle and a newly developed \emph{HistoryFinder oracle}—by combining automated analysis with expert-guided manual validation. We also introduce \textit{HistoryFinder}, a new method history generation tool designed to improve not only the accuracy and completeness of method change histories but also to offer competitive runtime performance. Through extensive evaluation across 400 methods from 40 open-source repositories, we show that \textit{HistoryFinder} consistently outperforms \textit{CodeShovel}, \textit{CodeTracker}, \textit{IntelliJ}, and \texttt{Git-based} baselines in terms of precision, recall, and F1 score. Moreover, \textit{HistoryFinder} achieves competitive runtime performance, offering the lowest mean and median execution times among all the research-based tools. While \texttt{Git-based} tools exhibit the fastest runtimes, this efficiency comes at the cost of significantly lower precision and recall—leaving \textit{HistoryFinder} as the best overall choice when both accuracy and efficiency are important. To facilitate adoption, we provide a web interface, CLI, and Java library for flexible usage.

\input{1-introduction}
\input{2-background-and-related-work}
\input{3-developing oracle}
\input{4-history-finder}
\input{5-evaluation-of-all-tools}
\input{6-discussion}
\input{7-conclusion}
